Deep Learning

### 2015-01-31 deepreview.tex
fixed the 'metaphors' citation (now Lakoff+Johnson-2008)

This rather naive way of performing machine translation has quickly become
competitive with the state-of-the-art and this raises serious doubts about
whether understanding a sentence requires anything like internal symbolic
expressions that are manipulated by binding their symbols to variables
in judiciously chosen rules of inference, as was previously thought by
many early AI researchers.  The encoder-decoder translation
networks do not work by using internal rules of inference in which
variables get bound to symbols. They just use big state vectors, big weight
matrices and scalar non-linearities to get the job done.  
Deriving conclusions using only the form of the premises (which is
what formal logic does) is a powerful
technique that people can eventually master, but the translation
results with recurrent neural networks suggest that it may not be a good model of
the way we normally reason or understand language. Recurrent neural
networks that represent thoughts as big vectors are more compatible with
the view that everyday reasoning involves many simultaneous analogies that
each contribute plausibility to a conclusion~\citep{metaphors,Rogers+McClelland-book2004}.

@@

However, even with good hand-crafted features, many interesting tasks
cannot be solved by linear classifiers. By distorting the space
as in Figure~\ref{fig:space-distortion}, a linear discrimination
becomes possible.
\iffalse
A common method to get around this
problem is to transform the feature vector into a higher dimensional vector
(i.e., corresponding to a much larger set of features)
through a non-linear mapping, exploiting the fact that collections of
vectors are more likely to be easily separated when they are spread around
a high-dimensional space~\citep{Cover65}. When there are at least
as many dimensions as examples, a linear classifier can always separate the
training examples, and one clever way to obtain a very high-dimensional space is to use a
``kernel function'' that measures the similarity between two vectors.
Using the kernel function, any input vector, ${\bf x}_i$ in the training
set can be used to define a feature whose activation for a new input
vector, ${\bf x}_{\rm new}$ is just the similarity between ${\bf x}_i$ and
${\bf x}_{\rm new}$. Given a kernel function, it is possible to jointly
optimize the choice of training examplars used to define features and the
class-specific weights associated with the features~\citep{Boser92}. The training
examplars used to define features are called ``support vectors'' and Support
Vector Machines~\citep{Boser92} have been very successful, especially for
tasks with a relatively small number of training examples in which features
are individually informative. They do not, however, perform well for tasks
such as object recognition in which the input space is high-dimensional and
the input-output mapping is so complex that computing similarities using a
simple kernel function is ineffective. 
%% THE TEXT BELOW IS NICE BUT TOO MUCH DETAIL ABOUT  SVMS FOR THIS
%% REVIEW.  
%% With a general-purpose feature space
%% and kernel (such as the Gaussian kernel), generalization far from the
%% examples is poor~\citep{Bengio-localfailure-NIPS-2006-small}, which is problematic
%% in high-dimensional spaces. However, kernel machines would perform well if a
%% very good set of features were provided: learning very good
%% features is what deep learning can do.
\fi

>>>>

This rather naive way of performing machine translation has quickly become
competitive with the state-of-the-art and this raises serious doubts about
whether understanding a sentence requires anything like internal symbolic
expressions that are manipulated by binding their symbols to variables
in judiciously chosen rules of inference, as was previously thought by
many early AI researchers.  The encoder-decoder translation
networks do not work by using internal rules of inference in which
variables get bound to symbols. They just use big state vectors, big weight
matrices and scalar non-linearities to get the job done.  
Deriving conclusions using only the form of the premises (which is
what formal logic does) is a powerful
technique that people can eventually master, but the translation
results with recurrent neural networks suggest that it may not be a good model of
the way we normally reason or understand language. Recurrent neural
networks that represent thoughts as big vectors are more compatible with
the view that everyday reasoning involves many simultaneous analogies that
each contribute plausibility to a 
conclusion~\citep{Lakoff+Johnson-2008,Rogers+McClelland-book2004}.

@@

However, even with good hand-crafted features, many interesting tasks
cannot be solved by linear classifiers. By distorting the space
as in Figure~\ref{fig:backprop-box} (top left), a linear discrimination
becomes possible.
\iffalse
A common method to get around this
problem is to transform the feature vector into a higher dimensional vector
(i.e., corresponding to a much larger set of features)
through a non-linear mapping, exploiting the fact that collections of
vectors are more likely to be easily separated when they are spread around
a high-dimensional space~\citep{Cover65}. When there are at least
as many dimensions as examples, a linear classifier can always separate the
training examples, and one clever way to obtain a very high-dimensional space is to use a
``kernel function'' that measures the similarity between two vectors.
Using the kernel function, any input vector, ${\bf x}_i$ in the training
set can be used to define a feature whose activation for a new input
vector, ${\bf x}_{\rm new}$ is just the similarity between ${\bf x}_i$ and
${\bf x}_{\rm new}$. Given a kernel function, it is possible to jointly
optimize the choice of training examplars used to define features and the
class-specific weights associated with the features~\citep{Boser92}. The training
examplars used to define features are called ``support vectors'' and Support
Vector Machines~\citep{Boser92} have been very successful, especially for
tasks with a relatively small number of training examples in which features
are individually informative. They do not, however, perform well for tasks
such as object recognition in which the input space is high-dimensional and
the input-output mapping is so complex that computing similarities using a
simple kernel function is ineffective. 
%% THE TEXT BELOW IS NICE BUT TOO MUCH DETAIL ABOUT  SVMS FOR THIS
%% REVIEW.  
%% With a general-purpose feature space
%% and kernel (such as the Gaussian kernel), generalization far from the
%% examples is poor~\citep{Bengio-localfailure-NIPS-2006-small}, which is problematic
%% in high-dimensional spaces. However, kernel machines would perform well if a
%% very good set of features were provided: learning very good
%% features is what deep learning can do.
\fi
